Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-14 resolution.tex
edits

@@

@@

To understand the degree to which atmospheric stability in the deep tropics is dependent on ascending and descending motion, temperature and moisture profiles are conditionally sampled based on whether $\langle \omega \rangle$ is positive or negative, indicating predominantly subsiding or ascending grid columns. The mean temperature and moisture profiles of subsiding and ascending regions in the deep tropics are used to compute the dilute-CAPE used by the ZM scheme, offline. Figure~\ref{fig:cape}a indicates that the mean profile of ascending regions are associated with large values of CAPE ($>170$ J/kg), and low values in subsiding regions ($<110$ J/kg). Figure~\ref{fig:profiles} shows the climatological temperature and specific humidity profiles of subsiding grid cells, averaged over the deep tropics and presented as anomalies from the mean temperature and specific humidity of the entire deep Tropics. The mean profiles of subsiding regions have an anomalous warming layer in the $600-800$ hPa layer and an anomalous moisture deficit throughout the entire column. This warming of the environment in subsiding regions opposes the generation of CAPE through equation~\ref{eq:cape}.

@@

>>>>

\subsection{Convection Activity and Atmospheric Stability}

@@

 \begin{table}
 \caption{Fractional contribution of the deep Tropics ($\pm 15^{\circ}$) to changes in global mean precipitation with resolution. The deep Tropics accounts for a majority of the resolution sensitivity despite being only about $25\%$ of the area of the planet. The grid headers refer to differences with respect to the next lowest grid resolution, e.g., $ne30 = ne30-ne20$, $ne40=ne40-ne30$, etc...}
 \centering
 \scriptsize
 \begin{tabular}{lcccccc}
   \hline
   Variable & $ne30$ & $ne40$ & $ne60$ & $ne80$ & $ne120$ \\ 
   \hline
   Convective Precipitation & 0.22 & 0.75 & 0.73 & 0.79 & 0.72 \\
   Stratiform Precipitation & 0.46 & 0.64 & 0.71 & 0.70 & 0.49 \\      
 \hline
 \end{tabular}
 \label{tbl:table2}
 \end{table}

@@

To understand the degree to which atmospheric stability in the deep tropics is dependent on ascending and descending motion, temperature and moisture profiles are conditionally sampled based on whether $\langle \omega \rangle$ is positive or negative, indicating predominantly subsiding or ascending grid columns. The mean temperature and moisture profiles of subsiding and ascending regions in the deep tropics are used to compute the dilute-CAPE used by the ZM scheme, offline. Figure~\ref{fig:cape}a indicates that the mean profile of ascending regions are associated with large values of CAPE ($>180$ J/kg), and low values in subsiding regions ($<110$ J/kg). Figure~\ref{fig:profiles} shows the climatological temperature and specific humidity profiles of subsiding grid cells, averaged over the deep tropics and presented as anomalies from the mean temperature and specific humidity of the entire deep Tropics. The mean profiles of subsiding regions have an anomalous warming layer in the $600-800$ hPa layer and an anomalous moisture deficit throughout the entire column. This warming of the environment in subsiding regions opposes the generation of CAPE through equation~\ref{eq:cape}.

@@

\subsection{Vertical Velocities and Stratiform Precipitation}

\subsection{Biases Unrelated to Resolution}
